Operation Manual

### 2024-10-01 docs/writing/operation_manual.tex
Adding figures and more nuance to instructions

\documentclass{article}
\usepackage[top=1.00in, bottom=1.0in, left=1in, right=1in]{geometry}
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}
\begin{document}
\section {Operation Manual}
\begin{outline}[enumerate]

\1 Device Setup

@@

	\item Turn on the Jetson by plugging the power port in
	\item Turn on the motor controller with the switch
	\item Turn on the power supply with the switch 
	\item Ensure everything is plugged in correctly

@@

        \item USB ring light is powered

@@

        \item Open Terminal

@@

@@

    \item Use the GUI to connect to establish a connection between the Jetson and the motor controller

@@

        \item Press the physical 'Reset' button on the motor controller
        \item Click the 'Serial Connect' button on the GUI and wait until the GUI is responsive again.
        \item Test that the connection has been made by clicking the arrows to manually jog the machine 

@@

        \item Click the 'Set Home' button on the GUI. This will move the machine towards the limit switches until they are triggered

@@

		\item Place the bullseye level on top of the sample

@@

        \item Loosen the lone screw until the bubble is centered on the bullseye

@@

		\item Level all samples and make sure to note their sample identifiers and relative positions on a piece of paper 
\item Capturing samples

@@

@@

    \item 

@@

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage[top=1.00in, bottom=1.0in, left=1in, right=1in]{geometry}
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}
\title {Operation Manual}
\begin{document}
\maketitle
\begin{outline}[enumerate]

\1 {Device Setup}

@@

	\item Turn on the Jetson by plugging the power port in. See Figure \ref{fig:jetson1}.
	\item Turn on the motor controller with the switch. See Figure \ref{fig:controller3}.
	\item Turn on the power supply with the switch. See Figure \ref{fig:power1}.
	\item Ensure everything is plugged in correctly. 

@@

        \item USB ring light is powered. It's best NOT to power it with the USB ports on the Jetson.

@@

        \item Open Terminal. See Figure \ref{fig:terminal1}

@@

                \item sudo chmod 777 /dev/ttyUSB0

@@

    \item Use the GUI to connect to establish a connection between the Jetson and the motor controller. See Figure \ref{fig:gui1}

@@

        \item Press the physical 'Reset' button on the motor controller. See Figure \ref{fig:controller3}
        \item Click the 'Serial Connect' button on the GUI and wait until the GUI is responsive again.  See Figure \ref{fig:gui1}
        \item Test that the connection has been made by clicking the arrows to manually jog the machine. See Figure \ref{fig:gui1}

@@

        \item Click the 'Set Home' button on the GUI. This will move the machine towards the limit switches until they are triggered.  See Figure \ref{fig:gui1}

@@

		\item Place the bullseye level on top of the sample. See Figure \ref{fig:level1}

@@

        \item Loosen the lone screw until the bubble is centered on the bullseye. See Figure \ref{fig:level2}

@@

\item Capturing Samples

@@

    \item Click 'Add Cookie'
            \item Once the boundaries are looking inclusive of the entire sample, add the cookie sample.
            \item If you only want to do one cookie, now you can click 'Capture All Cookies'. If not, continue to Multiple Samples.
		\item Repeat the sample levelling process for each cookie. Then repeat the Capturing Samples process. When you are ready click 'Capture All Cookies'
        \item Note that it's possible for the device to fail when stitching cookies. If this happens it will nullify your work setting up the cookies unfortunately. 
    \item Cookies vs. Cores
            \item The process remains mainly the same for capturing cores and cookies.
            \item The main difference would be that if you can see the entire width of the core in one image, make the height OR width equal to zero.
            \item Because a core holder is very close in height to the core itself, this can mess up the focusing control. 
            \item Before doing a lot of cores, test out one at a time to dial in settings and confirm that the stitch is working alright.

@@

    \item Failing before capturing all samples
            \item If this occurs, you'll have to check which cookies were completed and remove them from the table. Restart the adding samples step. 
            \item If this happens a lot, let Adam know.

@@

    \item Unresponsive GUI
            \item Close the terminal. This will force everything to close and end the process that is causing the delay. If this keeps happening let Adam know.

    \end{enumerate}
\item Figures 
    \begin{figure}
        \includegraphics[width=\linewidth]{../content/jetson.jpg}
        \caption{Jetson Orin Nano with all the ports connected.}
        \label{fig:jetson1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/motor_controller.jpg}
        \caption{Blackbox X32 Motor Controller from above.}
        \label{fig:controller1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/motor_controller_connections.jpg}
        \caption{Blackbox X32 Motor Controller fully connected ports.}
        \label{fig:controller2}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/motor_controller_buttons.jpg}
        \caption{Blackbox X32 Motor Controller buttons.}
        \label{fig:controller3}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/power_supply.jpg}
        \caption{Power supply fully connected.}
        \label{fig:power1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/sample_before_level.jpg}
        \caption{Cookie with the bubble of the level pointed directly towards the side of the table with one screw.}
        \label{fig:level1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/sample_levelled.jpg}
        \caption{Cookie with the bubble of the level centered.}
        \label{fig:level2}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/gui.jpg}
        \caption{Default GUI appearance after launching.}
        \label{fig:gui1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/background.jpg}
        \caption{Background after logging into the Jetson.}
        \label{fig:background1}
    \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth]{../content/terminal_commands.jpg}
        \caption{Background after logging into the Jetson.}
        \label{fig:terminal1}
    \end{figure}
